---
title: "Wine Arbitrage"
author: "Nikita Tkachenko"
date: "3/9/2022"
output:
  md_document: 
    toc: TRUE
    toc_depth: 3
bibliography: packages.bib
---

```{r setup, echo = FALSE}
knitr::opts_chunk$set(echo = FALSE,echo=FALSE,warning=FALSE,message=FALSE,error=FALSE)
knitr::write_bib(c(.packages()), "packages.bib")
```
## Abstract
Is there a correlation between wine's price and wine's signifiers such as rating, number of ratings, and country? To answer the question, 10,000 data points on wines were web scraped from Vivino. The data was cleaned and prepared for linear regression. A significant relationship between the explanatory variables and price was found. Additionally, a logistic regression on whether the wine's rating is above the mean wine rating was conducted. The logistic regression had significant predictive power. A simple rule of thumb is proposed from the research for buying wine in California.

## Introduction
Purchasing a bottle of wine is a heavy responsibility. The quality of the event depends on this small decision. But what if you do not know anything about wine? Is there a way to make a safe decision? Is more expensive wine better? I have web scraped over 10,000 red wines in $4 to $30 price range from Vivino.com to answer these questions. The first section will contain a description of the data collection process. The second section will discuss and visualize the data used in the analysis. The empirical model will be outlined in the third section, followed by a discussion of results and diagnostics in the fourth. The conclusion will contain possible future developments and my opinion on the project.
```{r Packages}
#
library(knitr)
# Packages for web scraping
library(rvest)
library(RSelenium)
# A collection of packages for data cleaning, manipulation and visualization
library(tidyverse)
# Will be used once for stri_split_fixed()
library(stringi)
# Packages that enhance ggplot2 (from tidyverse) functionality. They will be used to create groups of plots
library(cowplot)
library(ggforce)
# Package for working with dates
library(lubridate)
# to do White Test on heteroskedacity
library(lmtest)
# For VIF
library(car)
# For ROC curve 
library(pROC)
# Robust Linear
library(estimatr)
# For output formating
library(scales)
# HTML tables
library(sjPlot)
library(sjmisc)
library(sjlabelled)
```
## Data Description

### Vivino Web Scraping
A wine rating is a readily accessible measure of consumer sentiment and often the only way to suppose if the wine is good. Vivino is an online wine marketplace with over 12.5 million different wines and an active community. Wine cards have geographical information such as country, region and winery as well as information about the number of ratings, rating, vintage, and price. It must be noted that data were collected in San Francisco, California, and is specific to this location. Data was collected using docker, Rselenium, and rvest combination, so every listing would be exactly what you would find yourself. Each one-dollar price range (4-30) was scraped individually. For more information on the web scraping, please, refer to the datasource.r file.
```{r Web Scraping, include = FALSE, eval = FALSE}
# Web Scraping

# https://docs.ropensci.org/RSelenium/articles/docker.html#using-selenium-docker-images
# use firefox 2.53.1 (not 2.53.0)
# Put this into docker
# docker run -d -p 4445:4444 -p 5901:5900 selenium/standalone-firefox-debug:2.53.1
# tightVNC 192.168.99.100:5901 password: secret
# to stop docker: docker stop $(docker ps -q)
# RSelenium with Firefox

# Manually gather URLs for each price step
red_url <-c("https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1UctNrLA1VUuutA0NVksGEi5qBUC59DTbssSizNSSxBy1_KIU28TiZLX8pErbgqLM5FS18pLoWKCiYtvkRACB6xic",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1VctNrLA1U0uutA0NVksGEi5qBUC59DTbssSizNSSxBy1_KIU28TiZLX8pErbgqLM5FS18pLoWKCiYtvkRACCZxie",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1U8tNrLA1V0uutA0NVksGEi5qBUC59DTbssSizNSSxBy1_KIU28TiZLX8pErbgqLM5FS18pLoWKCiYtvkRACC4xig",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1V8tNrLC1UEuutA0NVksGEi5qBUC59DTbssSizNSSxBy1_KIU28TiZLX8pErbgqLM5FS18pLoWKCiYtvkRACDXxii",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLO1UMtNrLC1VEuutA0NVksGEi5qBUC59DTbssSizNSSxBy1_KIU28TiZLX8pErbgqLM5FS18pLoWKCiYtvkRACD2xik",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLO1VMtNrLA1NFBLrrQNDVZLBhIuagVAyfQ027LEoszUksQctfyiFNvE4mS1_KRK24KizORUtfKS6FigomLb5EQAklwYzQ%3D%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1NFDLTaywNTRUS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKANGPY%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1BFKJFbaGRmrJlbahwWrJQMJFrQAom55mW5ZYlJlakpijll-UYptYnKyWn1RpW1CUmZyqVl4SHQtUVGybnAgAoIoY-A%3D%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1NFLLTaywNTRWS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKEHGPo%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1NFbLTaywNTRRS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKGEGPw%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1NFHLTaywNTRVS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKIBGP4%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1NFXLTaywNTRTS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKJ-GQA%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1NFPLTaywNTRXS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKL7GQI%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1NFfLTaywNbRQS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKN4GQQ%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1tFDLTaywNbRUS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKP1GQY%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1tFTLTaywNTJQS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKJgGP8%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1MlDLTaywNTJUS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKCMGPg%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1AlKJFbZGRmrJlbahwWrJQMJFrQAom55mW5ZYlJlakpijll-UYptYnKyWn1RpW1CUmZyqVl4SHQtUVGybnAgAoQkY-g%3D%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1MlLLTaywNTJWS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKGGGPw%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1MlbLTaywNTJRS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKIDGP4%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1MlHLTaywNTJVS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKKAGQA%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1MlXLTaywNTJTS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKL9GQI%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1MlPLTaywNTJXS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKN6GQQ%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1MlfLTaywNbJQS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKP3GQY%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1slDLTaywNbJUS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKR0GQg%3D",
            "https://www.vivino.com/explore?e=eJzLLbI1VMvNzLM1slTLTaywNTZQS660DQ1WSwYSLmoFQNn0NNuyxKLM1JLEHLX8ohTbxOJktfykStuCoszkVLXykuhYoKJi2-REAKLfGQE%3D"
            ) #$4-$30

# Set up the data frame
dirty_wine <-data.frame(wine_name = as.character(),
                        wine_year = as.numeric(),
                        wine_country = as.character(),
                        wine_region = as.character(),
                        winery = as.character(),
                        wine_rating = as.numeric(),
                        n_ratings = as.numeric(),
                        wine_price = as.numeric())

# Code for webscraping
for (url in red_url) {
remDr <- remoteDriver(
  remoteServerAddr = "192.168.99.100",
  port = 4445L
)
remDr$open(silent = TRUE)
remDr$navigate(url)


# Scroll 20 time to load the page
for(i in 1:20){      
  remDr$executeScript(paste("scroll(0,",i*10000,");"))
  Sys.sleep(3)
  print(i)
}

# Get the page source
web <- remDr$getPageSource()
web <- xml2::read_html(web[[1]])

# Close RSelenium
remDr$close()
gc()
system("taskkill /im java.exe /f", intern=FALSE, ignore.stdout=FALSE)

# Now we use rvest to scrape the data
wine_country_raw <- web %>% html_nodes('.wineInfoLocation__regionAndCountry--1nEJz') %>% html_text() # region + country
wine_country_raw[wine_country_raw == ", "] <- "NA, NA"
wine_rating <- web %>% html_nodes('.vivinoRating__averageValue--3Navj') %>% html_text()
n_ratings_raw <- web %>% html_nodes('.vivinoRating__caption--3tZeS') %>% html_text()
wine_price_raw <- web %>% html_nodes('.addToCart__ppcPrice--ydrd5') %>% html_text()
# Wines that can be purchased through Vivino are wrapped into a button. Because they go first, we will simply bind it at the top of the price vector later.
wine_price_raw_button <- web %>% html_nodes(".addToCartButton__prefix--3LzGf+ div")%>% html_text()
# winery + grape + year
wine_name_raw <- web %>% html_nodes(".wineInfoVintage__truncate--3QAtw")%>% html_text() 

# Clean the scraped vectors
wine_price <- gsub("Available online from |\u20bd|,|[^0-9.-]", "",wine_price_raw)
wine_price_button <- gsub("Available online from |\u20bd|,|[^0-9.-]", "",wine_price_raw_button)
n_ratings <- gsub(" ratings", "",n_ratings_raw)
winery <- gsub("\\s*\\([^\\)]+\\)", "",matrix(data = wine_name_raw ,ncol=2,byrow = T)[,1])

wine_year <- matrix(data = wine_name_raw ,ncol=2,byrow = T)[,2] %>% str_sub(start = -4)
wine_name <- gsub("\\s*\\([^\\)]+\\)", "",matrix(data = wine_name_raw ,ncol=2,byrow = T)[,2] %>% str_sub(end = -6))

a<-wine_country_raw %>% stri_split_fixed(pattern = ", ", n = 2) %>% unlist() %>% matrix(ncol=2, byrow = T)

wine_country <- a[,2]
wine_region <- a[,1]

# Create data fram from the scraped page
df<-data.frame(wine_name = as.character(wine_name),
           wine_year = as.numeric(wine_year),
           wine_country = as.character(wine_country),
           wine_region = as.character(wine_region),
           winery = as.character(winery),
           wine_rating = as.numeric(wine_rating),
           n_ratings = as.numeric(n_ratings),
           wine_price = as.numeric(c(wine_price_button,wine_price))
           )

# Bind it with the main data frame
dirty_wine <- rbind(dirty_wine,df)
}

# Distinct and complete cases
df_wine <- dirty_wine[complete.cases(dirty_wine),] %>% distinct()
```

### Cleaning
The resulting dataset contains `r nrow(dim)` observations of red wine in the \$4 to \$30 price range. Wine year was replaced with years old as of the current year (2022). Countries with less than ten wines were removed. In the data used for regression, only wines younger than ten years and with more than 30 reviews were used.
```{r Data Cleaning}
# Download data
df_wine <- read.csv("red_wine4_30.csv")
# Complete cases
wines <- df_wine[complete.cases(df_wine),]
# age of wine
wines[,"y_old"] <- year(Sys.Date())-wines$wine_year 
# create wine type + country pairs (incase data has more then one type of wine)
wines$tc <- paste(wines$type,wines$wine_country) 
# count wine type + country pairs
include <- as.data.frame(table(wines$tc)) 
# Vector of rows to include
include<- include[include$Freq >10,] 
# Filter
wines <- wines[wines$tc %in% include$Var1,] 
#Select the necessary columnsof interests
wines <- wines[,c(2,4,7,8,9,10,6)] 
summary(wines)
```

### Data Exploration
The relationship between the wine price and explanatory variables is summarized in the following graphs. There is an observable correlation between rating and price. Cheaper wines appear to have more reviews. There seems to be some relationship between age and price, with older wines costing more. Countries have different distributions of prices.

```{r Plots, out.width = '100%',fig.align= 'center'}
# Build scatter and box plots to visualize relationship between wine price and explanatory variables
sp1 = wines %>% ggplot(aes(x=wine_rating, y = wine_price))+
  geom_point( color = "blue", alpha=0.2)+
  geom_smooth()+ ylab("Price") + xlab("Rating")
sp2 = wines %>% ggplot(aes(x=n_ratings, y = wine_price))+
  geom_point( color = "blue", alpha=0.2)+
  geom_smooth()+ ylab("Price") + xlab("Number of Ratings")
sp3 = wines %>% filter(y_old <=20) %>%ggplot(aes(x=y_old, y = wine_price))+
  geom_point( color = "blue", alpha=0.2)+
  geom_smooth()+ ylab("Price") + xlab("Age")

bp1 = wines %>% ggplot(aes(x=wine_rating, y = wine_price, group = wine_rating))+
  geom_boxplot( color = "blue", alpha=0.2) + ylab("Price") + xlab("Rating")
bp3 = wines %>% filter(y_old <=20)%>% ggplot(aes(x=y_old, y = wine_price, group = y_old))+
  geom_boxplot( color = "blue", alpha=0.2) + ylab("Price") + xlab("Age")
bp4 = wines %>% ggplot(aes(x=wine_country, y = wine_price))+
  geom_boxplot( color = "blue", alpha=0.2)+ ylab("Price") + xlab("Country")+theme(axis.text.x = element_text(angle = 90, vjust =0.1, hjust=0.2, size =6))

# Present plots all together
cowplot::plot_grid(sp1,sp2,sp3,bp1,bp4,bp3)
```

The following tables present distributions of explanatory variables. Wine ratings appear to be normally distributed, which might reflect Vivino's recommendation algorithm. Low wine ratings appear to be prevalent, with a large portion settled before 500 reviews. Most of the dataset's wines lay between the 1-5 age range, which can be expected for the price range. Lastly, products of some countries are more present in the sample due to the geographic position of the collection or simply the larger variety produced by the government. The distribution on the number of ratings appears to follow log distribution, so it will be used as a log in the regression.

```{r Frequency_Distributions,fig.show="hold", out.width= "50%"}
# Explore frequency of variables
hist(x=wines$wine_rating,freq = T,
     main="Wine Rating Distribution",
     xlab="Wine Rating")
# Number of rating distribution
hist(x=wines$n_ratings, freq = T,xlim = c(0,5000),breaks = 300,
     main="Number of ratings distribution",
     xlab="number of ratings bins")
#hist(x=wines[wines$n_ratings <= 500,"n_ratings"], freq = F,xlim = c(0,500),breaks = 20)
# Distribtuion of wines' ages
qplot(x = y_old, data = wines, geom="bar",xlim = c(0,20))+
  labs(title = "Wines from Countries")+ ylab("Number of Observations") + xlab("Age")
# Wine country
wines %>% group_by(wine_country) %>% summarise(n =n()) %>% 
  ggplot(aes(x = reorder(wine_country, -n), y= n))+
  geom_bar(position = 'dodge', stat='identity') +
  geom_text(aes(label=n), position=position_dodge(width=0.9), vjust=-0.25)+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.6)) + 
  labs(title = "Wines from Countries")+ ylab("Number of Observations") + xlab("")
```

The range of age variable might come from non-available for purchase or bad stock wines. The following graph examines if age leads to higher rating for each country. For some countries there is not enough data points to make a definitive answer. Nonetheless, in most cases wines younger than 5 years have higher ratings.

```{r RatingCountry, out.width = '80%', echo=FALSE,warning=FALSE,message=FALSE,error=FALSE, results='hide',fig.keep='all'}
# Relationship between age, wine rating and country
countries <-  wines %>% filter(y_old<=10)%>% select(wine_country) %>% unique() %>% as.vector
countries <- countries[[1]]
wines %>% filter(y_old<=10, wine_country == countries[1:7])%>%group_by(y_old, wine_country) %>% summarise(mean = mean(wine_rating))%>%
  ggplot(aes(x = y_old,y = mean))+geom_line()+stat_smooth(method= "lm")+facet_grid(cols = vars(wine_country))+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + 
  labs(title = "Rating, Age and Countries")+ ylab("Mean Rating") + xlab("Wine Age")

# break for markdown
layout(matrix(c(1,2), ncol=2), width=c(1,1))
par(mar=c(1,1,1,1))

wines %>% filter(y_old<=10, wine_country == countries[8:16])%>%group_by(y_old, wine_country) %>% summarise(mean = mean(wine_rating))%>%
  ggplot(aes(x = y_old,y = mean))+geom_line()+stat_smooth(method= "lm")+facet_grid(cols = vars(wine_country))+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) + 
  labs(title = "Rating, Age and Countries")+ ylab("Mean Rating") + xlab("Wine Age")

```

## Empirical Models
To estimate the relationships between variables I will be using linear model. The regression price prediction: `Price ~ age + age^2 + country + rating + log(number_of_ratings) rating*n_ratings`. Age and rating are expected to have a positive correlation, while number_of_ratings is suspected of having a negative correlation because affordable wines have more reviews. The variable country will be converted into a series of dummy variables, so some countries are generally expected to have better or worse wine, which will also be examined using logistic regression.

## Results and Diagnostics
```{r lm price modeles}
# Linear Model
# Select wines younger than 10 years and with more than 30 ratings
wines_price_lm <- wines %>% filter(y_old<=10, n_ratings >= 30)
lm_price_model <- lm(wine_price ~ y_old + y_old^2 + wine_country + log(n_ratings) + wine_rating + log(n_ratings) * wine_rating,data = wines_price_lm)


# Get TSS ESS RSS of Restricted
TSS = sum((wines_price_lm$wine_price - mean(wines_price_lm$wine_price))^2)
ESS = sum((lm_price_model$fitted.values - mean(wines_price_lm$wine_price))^2)
RSS = sum((wines_price_lm$wine_price - lm_price_model$fitted.values)^2)

M = length(countries <-  wines_price_lm$wine_country %>% unique())
k = length(lm_price_model$coefficients) -1
N = nobs(lm_price_model)
# Wald test
wald_test = (ESS/M)/(RSS/(N-k-1))
wald_test = round(wald_test,2)
```

The regression results suggest that age and `wine_rating` positively correlate with price, while `n_ratings` have negative. Each extra year increases the price by `r dollar(round(lm_price_model$coefficients["y_old"],2))`. A 1% increase in the number of ratings coincides with a `r percent(abs(round(lm_price_model$coefficients["log(n_ratings)"],6)/100), accuracy = 0.01)` decrease in price. The interaction variable between `n_ratings` and `wine_rating` suggests that 1 unit increase in rating increases marginal effect of 1% change of number of ratings on price by `r percent(abs(round(lm_price_model$coefficients["log(n_ratings):wine_rating"],6)/100), accuracy = 0.01)`. Three of these variables have a significant relationship at the 1% level. Countries have a variable impact on the price, with some being better than others. Wald Test on the significance of the country variable resulted in `r wald_test`, which is enough to accept that the country variable is significant at 1% significance. Level R^2^ of the regression is `r percent(summary(lm_price_model)$r.squared, accuracy = 0.01)`, meaning the variability of explanatory variables explains `r percent(summary(lm_price_model)$r.squared, accuracy = 0.01)` of the price variation. F statistic for the regression is `r round(summary(lm_price_model)$fstatistic, 2)["value"]`, which is enough to confirm that the regression has substantial explanatory power at 1% significance level. To test for heteroskedasticity, White Test was used. The test p-value is below 1%, so we can conclude that the distribution of errors is  heteroskedastic. To test for multicollinearity, VIF is used. All explanatory variables before introduction of interaction term had VIF less than 1.1, meaning multicollinearity was not a concern for the model. Nonetheless, introduction of interaction term reduced intercept and wine country Chile significance below threshold, which was expected. 

```{r LM Price, fig.keep='all'}
tab_model(summary(lm_price_model))
#print(aod::wald.test(Sigma = vcov(lm_price_model),b=coef(lm_price_model), Terms = 4))

print(paste("Wald test statistic:",round(wald_test,2)))

#res <- resid(lm_price_model)
#plot(fitted(lm_price_model), res)

lmtest::bptest(lm_price_model, ~ y_old * wine_country * log(n_ratings) * wine_rating + I(y_old^2)+I(wine_country)+I(wine_rating^2)+I(log(n_ratings)^2), data = wines_price_lm)

# VIF
car::vif(lm_price_model)
# Print distribution of residuals
yhat <- predict(lm_price_model, wines_price_lm)
y <- wines_price_lm[,5]
hist((yhat-y),breaks = 25)

```

To address the heteroskedasticity a robust regression was performed. The t-statistics were not significantly different from the original OLS regression, so we can conclude heteroskedasticity is not a major concern.
```{r LM Robust,  fig.keep='all'}
# Linear Model
# Select wines younger than 10 years and with more than 30 ratings
wines_price_lm <- wines %>% filter(y_old<=10, n_ratings >= 30)
lm_robust_model <- estimatr::lm_robust(wine_price ~ y_old + y_old^2 + wine_country + log(n_ratings) + wine_rating + log(n_ratings) * wine_rating, data = wines_price_lm,se_type = "stata")

#summary(lm_robust_model)
# 
# # Get TSS ESS RSS of Restricted
# TSS = sum((wines_price_lm$wine_price - mean(wines_price_lm$wine_price))^2)
# ESS = sum((lm_robust_model$fitted.values - mean(wines_price_lm$wine_price))^2)
# RSS = sum((wines_price_lm$wine_price - lm_robust_model$fitted.values)^2)
# 
# M = length(countries <-  wines_price_lm$wine_country %>% unique())
# k = length(lm_robust_model$coefficients) -1
# N = nobs(lm_robust_model)
# # Wald test
# wald_test = (ESS/M)/(RSS/(N-k-1))
# wald_test = round(wald_test,2)
# print(paste("Wald test statistic:",round(wald_test,2)))
# 
# #res <- resid(lm_price_model)
# #plot(fitted(lm_price_model), res)
# 
# lmtest::bptest(lm_robust_model, ~ y_old * wine_country * log(n_ratings) * wine_rating + I(y_old^2)+I(wine_country)+I(wine_rating^2)+I(log(n_ratings)^2), data = wines_price_lm)

# VIF
#car::vif(lm_robust_model)

V1 <- lm_robust_model %>% tidy() %>% select(statistic) %>% rename( "Robust" = statistic)
V2 <- lm_price_model %>% tidy() %>% select(statistic) %>% rename( "OLS" = statistic )
V0 <- names(lm_price_model$coefficients)

cbind(V1, V2) %>% as.data.frame() %>% round(3) %>% cbind(V0, .) %>% rename("coefficients" = V0) %>% kable()
```

### Is the wine good?
Another question is, would it possible to guess whether a wine is good? Let us divide wines into bad, below mean rating, and good, above mean rating. Logistic regression was run using price, age, and number of ratings to answer the question. The data was partitioned into 80% train and 20% test data. The resulting regression `good ~ y_old + y_old^2 + wine_country + log(n_ratings) + wine_price` found that at 1% significance level there is negative correlation with age and positive correlation with log of number of ratings and price. Only a few countries pass the 5% significance level.
Nonetheless, the Wald Test statistic of 420.92 suggests that the variable country is significant to be included in the regression. The R^2^ is 23.13%, meaning 23.13% of the variability in good/bad is explained by variance of explanatory variables. F statistic is 420.92, which is enough to confirm that the regression has substantial explanatory power at a 1% significance level. The area under the ROC curve is 78.1%, indicating that the model can distinguish between good and bad wines.

```{r LogRegressionGood, fig.keep='all', fig.align='center'}
# Building logistic regression
# Create condition whether wine has higher rating than mean
wines_glm <- wines %>% filter(y_old<=10, n_ratings >= 30) %>% mutate(good = ifelse(wine_rating>=mean(wine_rating),1,0))
# Create test and train datasets
smp_size <- floor(0.8 * nrow(wines_glm))
set.seed(123)
train_ind <- sample(seq_len(nrow(wines_glm)), size = smp_size)
train <- wines_glm[train_ind,]
test <- wines_glm[-train_ind,]
test_good <- test$good
# General Linear Model for good or bad wine
lmmodel <- lm(good ~ y_old + y_old^2 + wine_country + log(n_ratings) + wine_price,data = train, family = "binomial")
tab_model(lmmodel)
predicted = predict(lmmodel, test,type = "response")
#lmmodel2 <- lm(good ~ y_old + n_ratings + wine_price,data = train, family = "binomial")
#summary(lmmode12)
#car::linearHypothesis(lmmodel,"wine_country=0")

# Get TSS ESS RSS of Restricted
TSS = sum((train$wine_price - mean(train$wine_price))^2)
ESS = sum((lmmodel$fitted.values - mean(train$wine_price))^2)
RSS = sum((train$wine_price - lmmodel$fitted.values)^2)

M = length(countries <-  train$wine_country %>% unique())
k = length(lmmodel$coefficients) -1
N = nobs(lmmodel)
# Wald test
wald_test = (ESS/M)/(RSS/(N-k-1))
wald_test = round(wald_test,2)
print(paste("Wald test statistic:",round(wald_test,2)))

# Plot AUC curve
ROC <- pROC::roc(test$good,predicted)
plot(ROC, col = "red")
auc(ROC)


```

### So which country should I buy?
If you live in California, according to the t-test results, wines made in the U.S. have a significantly better rating on Vivino.

```{r AnyCountryBetter, results='hide',fig.keep='all',fig.align='center'}

### Does any country make better wine?
wines %>% group_by(wine_country) %>% summarise( sd = sd(wine_rating),mean = mean(wine_rating), freq = n()) %>%
  mutate(t = (mean-mean(wines$wine_rating))/(sd/freq^0.5)) %>% mutate(Ha = ifelse(t>2.56,T,F)) %>% arrange(desc(t))%>%
  ggplot (aes(x = wine_country, y = t, fill = Ha)) + geom_col() +
  labs(x = "Countries", y = "t statistic", title = "Wine ratings t-test", fill = "Better?")+
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=0.5))

```

## Conclusion
Searching for a good bottle of wine is not easy and might feel like rolling a dice. Luckily, there appears to be some correlation between ratings, prices, and countries. While it is impossible to make a 100% accurate prediction, devising a rule of thumb can be reasonable. If you live in California look for the U.S.-made wines and try to buy the most expensive you can reasonably afford, or download Vivino and check the reviews before buying.

There is a more efficient way to web scrape data from Vivino using their API. So, if someone wants to reproduce data collection, I would recommend going this route rather than the one I elected. Additionally, future development would involve incorporating weather data for the regions of the wines.

## References
<div id="refs"></div>
















